RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-01-04 jsac.tex
:triangular_flag_on_post: JSAC 230104

	% \begin{subsection}{Related Works}
	Similar to \gls{cr}, active-passive coexisting networks can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
	% To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, linear and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
	% However, it only considered the case where the primary and backscatter symbols of the same period are perfectly aligned in time.
	Joint \gls{ml} decoding provides the best error performance but requires prohibitive computational complexity especially for high-order modulations \cite{Yang2018}.
	Indeed, active-passive coexisting networks have three special and important properties:
	1) primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
	2) backscatter signal strength is much weaker than primary due to the \emph{double fading} effect;
	3) backscatter \emph{symbol period} is longer than primary due to the load switching constraint.
	% ! double modulation, double fading, symbol period difference
	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
	During primary decoding, the randomness of backscatter modulation can be modelled as channel uncertainty or multiplicative interference when the backscatter-over-primary symbol period ratio $N$ is large or small\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{10} and \num{1000}.}.
	Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive because it involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
	When $N$ is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding based on known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart, and both links may be decoded in an interference-free manner \cite{Long2020a}.
	On the other hand, efficient backscatter multiple access design remains an open issue for \gls{bc}.
	\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} where the \gls{sic} order depends on the backscatter channel strength, but the performance deteriorates fast as the number of nodes increases.
	\gls{tdma}-based \gls{sr} was also considered in \cite{Yang2021a} where each node transmits information during its dedicated slot and harvests energy otherwise.
	It enables adaptive transmission time and reflection ratio design but introduces extra coordination cost.
	\cite{Vougioukas2019} modifies the load-switching speed to shift the scattered signal to the desired frequency band.
	This enables backscatter \gls{fdma} at the cost of larger bandwidth and higher power consumption at the scatter nodes.
	To reduce the coordination cost, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
	This code-domain solution suffers from the near-far problem and imperfect synchronization, both being severe in \gls{bc}.

@@

	\emph{Second,} we address the first challenge by proposing a practical receiver that accommodates the double fading, double modulation, and symbol period difference of active-passive coexisting networks.
	Since joint decoding involves high complexity while individual decoding can be inefficient (neither cooperative nor exploiting signal properties), most relevant literatures consider a sequential primary-backscatter decoding based on \gls{sic}.
	Specifically, the decoding of each backscatter symbol requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.
	In contrast, the proposed RIScatter receiver semi-coherently decodes the backscatter symbol from the accumulated receive energy, re-encodes to recover the exact reflection pattern, and combine it with relevant \gls{csi} to determine the transmitter-scatter-receiver path response.
	Thanks to the double modulation and symbol period difference, the backscatter symbol can be modelled within primary channel (similar to \gls{ris}) rather than being re-precoded and cancelled, and the semi-coherent energy-based backscatter detection indeed becomes part of primary channel training.
	The strategy is suitable for arbitrary primary sampling rate and backscatter load-switching speed (i.e., arbitrary $N$).
	This is the first paper to consider such a sequential backscatter-primary decoding and treat semi-coherent backscatter detection as part of primary channel training.

@@

\begin{section}{RIScatter}
	% \begin{subsection}{Concepts}
	We propose RIScatter in Fig.~\subref*{fg:riscatter} as a generalization of \gls{bc} and \gls{ris}, which involves coexisting active primary and passive backscatter links in a flexible and mutualistic manner.
	RIScatter nodes leverage \gls{csi}- and \gls{qos}-based reflection state distribution design to smoothly transition between backscatter modulation and passive beamforming.
	Fig.~\ref{fg:riscatter_node} illustrates the block diagram, equivalent circuit, and scatter model of a RIScatter node.
	It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
	\begin{figure*}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.32\linewidth}{!}{
				\input{assets/illustration/block_diagram.tex}
			}
			\label{fg:block_diagram}
		}
		\subfloat[Equivalent Circuit]{
			\resizebox{0.37\linewidth}{!}{
				\input{assets/illustration/equivalent_circuit.tex}
			}
			\label{fg:equivalent_circuit}
		}
		\subfloat[Scatter Model]{
			\resizebox{0.28\linewidth}{!}{
				\input{assets/illustration/scatter_model.tex}
			}
			\label{fg:scatter_model}
		}
		\caption{
		Block diagram, equivalent circuit, and scatter model of a RIScatter node.
		The solid and dashed vectors represent signal and energy flows.
		The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
		}
		\label{fg:riscatter_node}
	\end{figure*}
	Fig.~\ref{fg:scatter_comparison} compares the reflection state distribution and reflection pattern of RIScatter and other applications.
	\begin{figure}[!t]
		\centering
		\subfloat[Reflection State Distribution]{
			\resizebox{0.32\columnwidth}{!}{
				\input{assets/illustration/input_distribution.tex}
			}
			\label{fg:input_distribution}
		}
		\subfloat[Reflection Pattern]{
			\resizebox{0.32\columnwidth}{!}{
				\input{assets/illustration/time_structure.tex}
			}
			\label{fg:time_structure}
		}
		\caption{
			Reflection state distribution and reflection pattern over time of \gls{bc}, \gls{ris}, and RIScatter.
			``PB'' means primary block and ``BB'' means backscatter block.
		}
		\label{fg:scatter_comparison}
	\end{figure}
	Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node \emph{semi-randomly} chooses the reflection state for each backscatter block with \emph{guidance of input probability} $P(\Gamma_m)$ at state $m$.
	Such an adaptive backscatter channel coding includes the degenerate distribution of \gls{ris} and the uniform distribution of line-coded \gls{bc} as special cases.
	Importantly, RIScatter system design only requires the \emph{direct} transmitter-receiver and \emph{cascaded} transmitter-scatter-receiver \gls{csi}.
	For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
	For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.

	% ? Add an illustration here if space allows
	We also propose a novel cooperative receiver that exploits the double modulation, double fading and symbol period difference to reduce the decoding complexity and improve the primary-backscatter tradeoff.
	As illustrated in Fig.~\ref{fg:energy_distribution}, conditioned on different reflection state hypotheses, the accumulated receive energy per backscatter block follows Gamma distribution with different scale parameters \cite{Qian2017b}.
	\begin{figure}[!t]
		\centering
		\resizebox{0.4\columnwidth}{!}{
			\input{assets/illustration/energy_distribution.tex}
		}
		\caption{
			\gls{pdf} of accumulated receive energy per backscatter block conditioned on different reflection state hypotheses.
			% $z$, $t$, $\mathcal{H}$ and $\mathcal{R}$ denote the accumulated receive energy, decision threshold, reflection state hypothesis, and decision regions, respectively.
		}
		\label{fg:energy_distribution}
	\end{figure}
	Hence, the receiver can semi-coherently (under primary uncertainty) decode RIScatter nodes from the accumulated receive energy, re-encode to recover the exact reflection patterns, and combine those with cascaded \gls{csi} to determine the multipath response and model within the primary channel.
	Such a backscatter-primary decoding enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison, re-encoding, and precoding during each backscatter (instead of primary) block.
	It enjoys a three-fold benefit compared to conventional primary-backscatter decoding with \gls{sic}, namely
	1) reduces the re-encoding frequencies to $1/N$;
	2) requires no re-precoding, cancellation, or \gls{mrc};
	3) preserves backscatter modulation and passive beamforming at smaller $N$ for potentially higher backscatter throughput.
	% \end{subsection}

@@

	Without loss of generality, let the backscatter-over-primary symbol period ratio $N$ be a positive integer.

@@

		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and above.
		\emph{First,} we observe both \gls{bbc} and \gls{sr} almost ensure noise-free backscatter transmission when $N$ is sufficiently large.
		For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmtmac} \eqref{eq:dmtmac} has lower error probabilities.
		For \gls{sic}-based \gls{sr}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\iota$ becomes insignificant.
		However, the primary rate is only maintained at a very large $N$, which significantly constrains the backscatter \emph{throughput}.
		\emph{Second,} the average primary rate slightly increases/decreases in the presence of a \gls{ambc}/\gls{ris} node, and the multipath benefit of \gls{sr} is unobvious.
		This is because the cascaded channel can be orders of magnitude weaker than the direct channel due to the double fading effect.
		\gls{ris} always ensures constructive superposition of direct and scattered components, while \gls{sr} only creates a quasi-static rich-scattering environment that \emph{stochastically} enhances the average primary rate.
		When $N$ is moderate, the randomly scattered signals should be modelled as primary interference rather than multipath components, and the \gls{sr} point will move towards the \gls{ambc} point.
		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff with adaptive input distribution design.
		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others with passive beamforming provided by deterministic reflection pattern.
		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is higher than \gls{ambc} but lower than \gls{bbc} and \gls{sr}.
		This is because both RIScatter and \gls{ambc} (resp. \gls{bbc} and \gls{sr}) employ semi-coherent (resp. coherent) energy detection, while RIScatter with adaptive channel coding can achieve higher backscatter rate than \gls{ambc} with equiprobable inputs.
		Importantly, such a practical RIScatter detection is feasible for arbitrary $N$, which unleashes the potential of fast-switching nodes.
		% , and using a fast-switching node with smaller $N$ can increase the backscatter throughput per unit time while preserving the dynamic passive beamforming gain on the primary link.
	\end{subsection}

@@

	\begin{subsection}{Rate Region under Different Configurations}
		\begin{figure}[!t]
			\centering
			\subfloat[RIScatter Nodes\label{fg:region_tags}]{
				\resizebox{0.27\columnwidth}{!}{
					\input{assets/simulation/region_tags.tex}
				}
			}
			\subfloat[Input States\label{fg:region_states}]{
				\resizebox{0.27\columnwidth}{!}{
					\input{assets/simulation/region_states.tex}
				}
			}
			\subfloat[Transmit Antennas\label{fg:region_txs}]{
				\resizebox{0.27\columnwidth}{!}{
					\input{assets/simulation/region_txs.tex}
				}
			}
			\\
			\subfloat[Symbol Period Ratio\label{fg:region_duration}]{
				\resizebox{0.27\columnwidth}{!}{
					\input{assets/simulation/region_duration.tex}
				}
			}
			\subfloat[Average Noise Power\label{fg:region_noise}]{
				\resizebox{0.27\columnwidth}{!}{
					\input{assets/simulation/region_noise.tex}
				}
			}
			\subfloat[Disk Radius\label{fg:region_coverage}]{
				\resizebox{0.27\columnwidth}{!}{
					\input{assets/simulation/region_coverage.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions for different system configurations.
			}
			\label{fg:region_config}
		\end{figure}
		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$ as a reference.
		\begin{subsubsection}{Number of Nodes}
			Fig.~\subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influence the primary-backscatter tradeoff.
			Interestingly, we observe that increasing $K$ has a larger benefit on the total backscatter rate than primary.
			This is because each RIScatter node not only affects the primary equivalent \gls{snr} but also influences the relative energy difference that other nodes can create.
			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that \emph{minimizes} the primary equivalent channel strength, in order to increase the backscatter rate of other nodes.
			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a classic passive array gain of $N^2$.
		\end{subsubsection}

@@

		\begin{subsubsection}{Symbol Period Ratio}
			Fig.~\subref*{fg:region_duration} presents how symbol period ratio $N$ affects the achievable rate region, where the unit of total backscatter rate is bits per primary block (to indicate throughput).
			Apparently, using a very large $N$ can severely constrain the backscatter throughput, since the gain in energy certainty (by law of large numbers) cannot withstand the loss in gross rate.
			As $N \to \infty$, RIScatter nodes boil down to \gls{ris} elements with fixed reflection pattern during whole channel block and the total backscatter rate approaches \num{0}.
			On the other hand, when $N$ is too small, the equivalent \gls{dmtmac} \eqref{eq:dmtmac} has very high error probabilities and the energy detection can be unreliable.
			It explains the observation that $N=10$ provides lower backscatter achievable rate than $N=20$, although nodes are encoding at higher gross rate.
			Therefore, we conclude the design of symbol period ratio $N$ in RIScatter systems should account for multiple factors (e.g., data rate requirements, physical constraints at the nodes, and signal processing capability at the user).
		\end{subsubsection}

>>>>

	% \begin{subsection}{Related Works}
	Similar to \gls{cr}, active-passive coexisting networks can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
	% To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, linear and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
	% However, it only considered the case where the primary and backscatter symbols of the same period are perfectly aligned in time.
	Joint \gls{ml} decoding provides the best error performance but requires prohibitive computational complexity especially for high-order modulations \cite{Yang2018}.
	Indeed, active-passive coexisting networks have three special and important properties:
	1) primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
	2) backscatter signal strength is much weaker than primary due to the \emph{double fading} effect;
	3) backscatter \emph{symbol period} is longer than primary due to the load switching constraint.
	% ! double modulation, double fading, symbol period difference
	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
	During primary decoding, the randomness of backscatter modulation can be modelled as either channel uncertainty or multiplicative interference, when the spreading factor (i.e., backscatter-over-primary symbol period ratio) $N$ is large or small, respectively\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed usually varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical spreading factor between \num{10} and \num{1000}.}.
	Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive because it involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
	When the spreading factor is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding based on known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart, and both links may be decoded in an interference-free manner \cite{Long2020a}.
	On the other hand, efficient backscatter multiple access design remains an open issue for \gls{bc}.
	\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} where the \gls{sic} order depends on the backscatter channel strength, but the performance deteriorates fast as the number of nodes increases.
	\gls{tdma}-based \gls{sr} was also considered in \cite{Yang2021a} where each node transmits information during its dedicated slot and harvests energy otherwise.
	It enables adaptive transmission time and reflection ratio design but introduces extra coordination cost.
	\cite{Vougioukas2019} modifies the load-switching speed to shift the scattered signal to the desired frequency band.
	This enables backscatter \gls{fdma} at the cost of larger bandwidth and higher power consumption at the scatter nodes.
	To reduce the coordination cost, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
	This code-domain solution suffers from the near-far problem and imperfect synchronization, both being severe in \gls{bc}.

@@

	\emph{Second,} we address the first challenge by proposing a practical receiver that accommodates the double fading, double modulation, and symbol period difference of active-passive coexisting networks.
	Since joint decoding involves high complexity while individual decoding can be inefficient (neither cooperative nor exploiting signal properties), most relevant literatures consider a sequential primary-backscatter decoding based on \gls{sic}.
	Specifically, the decoding of each backscatter symbol requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.
	In contrast, the proposed RIScatter receiver semi-coherently decodes the backscatter symbol from the accumulated receive energy, re-encodes to recover the exact reflection pattern, and combine it with relevant \gls{csi} to determine the transmitter-scatter-receiver path response.
	Thanks to the double modulation and symbol period difference, the backscatter symbol can be modelled within primary channel (similar to \gls{ris}) rather than being re-precoded and cancelled, and the semi-coherent energy-based backscatter detection indeed becomes part of primary channel training.
	The strategy is suitable for arbitrary primary sampling rate and backscatter load-switching speed (i.e., arbitrary spreading factor).
	This is the first paper to consider such a sequential backscatter-primary decoding and treat semi-coherent backscatter detection as part of primary channel training.

@@

\begin{section}{RIScatter}
	% \begin{subsection}{Concepts}
	We propose RIScatter in Fig.~\subref*{fg:riscatter} as a generalization of \gls{bc} and \gls{ris}, which involves coexisting active primary and passive backscatter links in a flexible and mutualistic manner.
	RIScatter nodes leverage \gls{csi}- and \gls{qos}-based reflection state distribution design to smoothly transition between backscatter modulation and passive beamforming.
	Fig.~\ref{fg:riscatter_node} illustrates the block diagram, equivalent circuit, and scatter model of a RIScatter node.
	It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
	\begin{figure*}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.32\linewidth}{!}{
				\input{assets/illustration/block_diagram.tex}
			}
			\label{fg:block_diagram}
		}
		\subfloat[Equivalent Circuit]{
			\resizebox{0.37\linewidth}{!}{
				\input{assets/illustration/equivalent_circuit.tex}
			}
			\label{fg:equivalent_circuit}
		}
		\subfloat[Scatter Model]{
			\resizebox{0.28\linewidth}{!}{
				\input{assets/illustration/scatter_model.tex}
			}
			\label{fg:scatter_model}
		}
		\caption{
		Block diagram, equivalent circuit, and scatter model of a RIScatter node.
		The solid and dashed vectors represent signal and energy flows.
		The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
		}
		\label{fg:riscatter_node}
	\end{figure*}
	Fig.~\ref{fg:scatter_comparison} compares the reflection state distribution and reflection pattern of RIScatter and other applications.
	\begin{figure}[!t]
		\centering
		\subfloat[Reflection State Distribution]{
			\resizebox{0.32\columnwidth}{!}{
				\input{assets/illustration/input_distribution.tex}
			}
			\label{fg:input_distribution}
		}
		\subfloat[Reflection Pattern]{
			\resizebox{0.32\columnwidth}{!}{
				\input{assets/illustration/time_structure.tex}
			}
			\label{fg:time_structure}
		}
		\caption{
			Reflection state distribution and reflection pattern over time of \gls{bc}, \gls{ris}, and RIScatter.
			``PB'' means primary block and ``BB'' means backscatter block.
			Spreading factor is 2 in this example.
		}
		\label{fg:scatter_comparison}
	\end{figure}
	Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node \emph{semi-randomly} chooses the reflection state for each backscatter block with \emph{guidance of input probability} $P(\Gamma_m)$ at state $m$.
	Such an adaptive backscatter channel coding includes the degenerate distribution of \gls{ris} and the uniform distribution of line-coded \gls{bc} as special cases.
	Importantly, RIScatter system design only requires the \emph{direct} transmitter-receiver and \emph{cascaded} transmitter-scatter-receiver \gls{csi}.
	For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
	For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.

	% ? Add an illustration here if space allows
	We also propose a novel cooperative receiver that exploits the double modulation, double fading and symbol period difference to reduce the decoding complexity and improve the primary-backscatter tradeoff.
	As illustrated in Fig.~\ref{fg:energy_distribution}, conditioned on different reflection state hypotheses, the accumulated receive energy per backscatter block follows Gamma distribution with different scale parameters \cite{Qian2017b}.
	\begin{figure}[!t]
		\centering
		\resizebox{0.4\columnwidth}{!}{
			\input{assets/illustration/energy_distribution.tex}
		}
		\caption{
			\gls{pdf} of accumulated receive energy per backscatter block conditioned on different reflection state hypotheses.
			% $z$, $t$, $\mathcal{H}$ and $\mathcal{R}$ denote the accumulated receive energy, decision threshold, reflection state hypothesis, and decision regions, respectively.
		}
		\label{fg:energy_distribution}
	\end{figure}
	Hence, the receiver can semi-coherently (under primary uncertainty) decode RIScatter nodes from the accumulated receive energy, re-encode to recover the exact reflection patterns, and combine those with cascaded \gls{csi} to determine the multipath response and model within the primary channel.
	Such a backscatter-primary decoding enables simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison, re-encoding, and precoding during each backscatter (instead of primary) block.
	It enjoys a three-fold benefit compared to conventional primary-backscatter decoding with \gls{sic}, namely
	1) reduces the re-encoding frequencies to $1/N$;
	2) requires no re-precoding, cancellation, or \gls{mrc};
	3) preserves backscatter modulation and passive beamforming at smaller spreading factors for potentially higher backscatter throughput.
	% \end{subsection}

@@

	Without loss of generality, let the spreading factor $N$ be a positive integer.

@@

		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and above.
		\emph{First,} we observe both \gls{bbc} and \gls{sr} almost ensure noise-free backscatter transmission when the spreading factor $N$ is sufficiently large.
		For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmtmac} \eqref{eq:dmtmac} has lower error probabilities.
		For \gls{sic}-based \gls{sr}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\iota$ becomes insignificant.
		However, the primary rate is only maintained at a very large spreading factor, which significantly constrains the backscatter \emph{throughput}.
		\emph{Second,} the average primary rate slightly increases/decreases in the presence of a \gls{ambc}/\gls{ris} node, and the multipath benefit of \gls{sr} is unobvious.
		This is because the cascaded channel can be orders of magnitude weaker than the direct channel due to the double fading effect.
		\gls{ris} always ensures constructive superposition of direct and scattered components, while \gls{sr} only creates a quasi-static rich-scattering environment that \emph{stochastically} enhances the average primary rate.
		When $N$ is moderate, the randomly scattered signals should be modelled as primary interference rather than multipath components, and the \gls{sr} point will move towards the \gls{ambc} point.
		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff with adaptive input distribution design.
		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others with passive beamforming provided by deterministic reflection pattern.
		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is higher than \gls{ambc} but lower than \gls{bbc} and \gls{sr}.
		This is because both RIScatter and \gls{ambc} (resp. \gls{bbc} and \gls{sr}) employ semi-coherent (resp. coherent) energy detection, while RIScatter with adaptive channel coding can achieve higher backscatter rate than \gls{ambc} with equiprobable inputs.
		Importantly, such a practical RIScatter detection is feasible for arbitrary spreading factor, which unleashes the potential of fast-switching nodes.
		% , and using a fast-switching node with smaller $N$ can increase the backscatter throughput per unit time while preserving the dynamic passive beamforming gain on the primary link.
	\end{subsection}

@@

	\begin{subsection}{Rate Region under Different Configurations}
		\begin{figure}[!t]
			\centering
			\subfloat[RIScatter Nodes\label{fg:region_tags}]{
				\resizebox{0.27\columnwidth}{!}{
					\input{assets/simulation/region_tags.tex}
				}
			}
			\subfloat[Input States\label{fg:region_states}]{
				\resizebox{0.27\columnwidth}{!}{
					\input{assets/simulation/region_states.tex}
				}
			}
			\subfloat[Transmit Antennas\label{fg:region_txs}]{
				\resizebox{0.27\columnwidth}{!}{
					\input{assets/simulation/region_txs.tex}
				}
			}
			\\
			\subfloat[Spreading Factor\label{fg:region_duration}]{
				\resizebox{0.27\columnwidth}{!}{
					\input{assets/simulation/region_duration.tex}
				}
			}
			\subfloat[Average Noise Power\label{fg:region_noise}]{
				\resizebox{0.27\columnwidth}{!}{
					\input{assets/simulation/region_noise.tex}
				}
			}
			\subfloat[Disk Radius\label{fg:region_coverage}]{
				\resizebox{0.27\columnwidth}{!}{
					\input{assets/simulation/region_coverage.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions for different system configurations.
			}
			\label{fg:region_config}
		\end{figure}
		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$ as a reference.
		\begin{subsubsection}{Number of Nodes}
			Fig.~\subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influence the primary-backscatter tradeoff.
			Interestingly, we observe that increasing $K$ has a larger benefit on the total backscatter rate than primary.
			This is because each RIScatter node not only affects the primary equivalent \gls{snr} but also influences the relative energy difference that other nodes can create.
			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that \emph{minimizes} the primary equivalent channel strength, in order to increase the backscatter rate of other nodes.
			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a classic passive array gain of $N^2$.
		\end{subsubsection}

@@

		\begin{subsubsection}{Spreading factor}
			Fig.~\subref*{fg:region_duration} presents how the spreading factor $N$ affects the achievable rate region, where the unit of total backscatter rate is bits per primary block (to indicate throughput).
			Apparently, using a very large $N$ can severely constrain the backscatter throughput, since the gain in energy certainty (by law of large numbers) cannot withstand the loss in gross rate.
			As $N \to \infty$, RIScatter nodes boil down to \gls{ris} elements with fixed reflection pattern during whole channel block and the total backscatter rate approaches \num{0}.
			On the other hand, when $N$ is too small, the equivalent \gls{dmtmac} \eqref{eq:dmtmac} has very high error probabilities and the energy detection can thus be unreliable.
			It explains the observation that $N=10$ provides lower backscatter achievable rate than $N=20$, although nodes are encoding at higher gross rate.
			Therefore, we conclude the design of spreading factor $N$ in RIScatter systems should account for multiple factors (e.g., data rate requirements, load switching constraints at the nodes, and signal processing capability at the user).
		\end{subsubsection}
